MSB106 - Assignment

### 2023-01-31 MSB106_Assignment.qmd
Commit.

---
title: "MSB106_Assignment"
author: "Sindre H. Øveraas, Alen Colakovic, Mona Lisa Jones & Sebastian M. Fløysand"
format:
 pdf:
  fontsize: "10"
  documentclass: article
  margin-left: 2cm
  margin-right: 2cm
papersize: A4
editor: visual
---

```{r, message=FALSE}
library(rgdal)
library(dplyr)
library(RSQLite)
library(sf)
library(tidyverse)
library(readr)
```

@@

```{r}
Commune_Data <- inner_join(NOR_KOMM, NOR_KOMM_2, by = "kommunenummer") |>
  select(kommunenummer, HubName, HubDist, Turnover_capita_retail_Omsetning)
```

```{r}
Dentist_Data <- inner_join(Dist_Mal_Dentist, Dist_CBD_Dentist, by = "fid") |>
  select(fid, Juridisk.n, Antall.ans, Sum.Drifts, Sum.salgsi, Driftsresu.y, osm_id.y, latlong.y, HubName.y, HubDist.y, HubName.x, HubDist.x) |>
  rename("DistMal" = HubDist.x, "DistCBD" = HubDist.y, "HubNameMal" = HubName.x, "HubNameCBD" = HubName.y)
```

@@

>>>>

---
title: "MSB106 - Assignment"
author: "Sindre H. Øveraas, Alen Colakovic, Mona Lisa Jones & Sebastian M. Fløysand"
format:
 pdf:
  fontsize: "10"
  documentclass: article
  margin-left: 2cm
  margin-right: 2cm
papersize: A4
editor: visual
---

```{r, message=FALSE}
library(rgdal)
library(dplyr)
library(RSQLite)
library(sf)
library(tidyverse)
library(readr)
library(ggplot2)
library(kableExtra)
```

@@

```{r}
Commune_Data <- inner_join(NOR_KOMM, NOR_KOMM_2, by = "kommunenummer") |>
  select(kommunenummer, HubName, HubDist, Turnover_capita_retail_Omsetning) |>
  rename("knr" = kommunenummer, "DistMal" = HubDist, "HubNameMal" = HubName, "Turnover_capita_retail" = Turnover_capita_retail_Omsetning)
```

```{r}
Dentist_Data <- inner_join(Dist_Mal_Dentist, Dist_CBD_Dentist, by = "fid") |>
  select(fid, Juridisk.n, Antall.ans, Sum.Drifts, Sum.salgsi, Driftsresu.y, osm_id.y, latlong.y, HubName.y, HubDist.y, HubName.x, HubDist.x) |>
  rename("DistMal" = HubDist.x, "DistCBD" = HubDist.y, "HubNameMal" = HubName.x, "HubNameCBD" = HubName.y, "Driftsres" = Driftsresu.y, "osm_id" = osm_id.y, "latlong" = latlong.y)
```

@@

```{r}
kable(summary(Commune_Data))
```

```{r}
kable(summary(Dentist_Data[3:12]))
```

```{r}
Commune_Data |>
  ggplot(aes(x = DistMal, y = Turnover_capita_retail, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "Turnover capita in retail per inhabitant") +
  theme_bw()
```

Might be more appropriate to explore the distance from CBDs to Malls compared to turnover capita in retail per inhabitant, rather than the distance from the geographical centroid of Norwegian Communes, because of the tendency of bigger population density around CBDs.

```{r}
Dentist_Data |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r}
Dentist_Data_LIMIT <- Dentist_Data |>
  filter(Sum.salgsi < 100000000, DistCBD < 250,
         Driftsres < 20000000, Driftsres > -10000000, DistMal < 80)
```

```{r}
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistCBD, y = Sum.salgsi, colour = DistCBD)) +
  geom_point(lwd = .9) + labs(x = "Distance from CBD", y = "Income") +
  theme_bw()
```

```{r}
Dentist_Data |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```

```{r}
Dentist_Data_LIMIT |>
  ggplot(aes(x = DistMal, y = Driftsres, colour = DistMal)) +
  geom_point(lwd = .9) +
  labs(x = "Distance from Mall", y = "EBIT") +
  theme_bw()
```
